% Autogenerated translation of about.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\setmainfont{Helvetica Neue}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\hrule
permalink: /
title: "Short bio"
excerpt: "About me"
author\emph{profile: true
redirect}from: 
  - /about/

\section*{  - /about.html}

I am a postdoctoral researcher at the \href{https://www.unige.ch/gsem/fr/recherche/corps-professoral/chercheurs/gloria-buritica-borda/}{Université de Genève}, in the Research group on Statistics of Prof. \href{http://www.sengelke.com}{Sebastian Engelke}. I previously completed my Ph.D. at the LPSM laboratory in Sorbonne Université in May 2022 under the supervision of Prof. \href{https://www.lsce.ipsl.fr/Phocea/Pisp/visu.php?id=176&uid=naveau}{Philippe Naveau} and Prof. \href{http://wintenberger.fr}{Olivier Wintenberger}. 

\href{/files/CV_BURITICA.pdf}{\emph{curriculum vitae}}, \href{mailto:gloria.buriticaborda@unige.ch}{\emph{e-mail}}.

\section*{News}

We are thrilled to announce the workshop \href{https://sites.google.com/view/causality-extremes}{\emph{Causality in Extremes}} to be held at the University of Geneva from February 14 - 16, 2024.
Registration is now open and closes on October 31, 2023.

\section*{My research}

I work in extreme value theory, where I study methodologies for assessing time dependencies in multivariate heavy-tailed series. I’m also interested in the link between extreme value theory and statistical learning. My current interest lies in improving machine learning techniques for predicting occurrences that did not happen in the training data. For this purpose, we can borrow the extrapolation strategies in extreme value theory.

I enjoy working on risk assessment with applications to environmental sciences and econometrics.

Outside the university, I love reading and a fresh just-grind cup of Colombian coffee. I specially enjoy gathering with friends and family around flavorful food and pursuing bucolic landscapes. 

\section*{Ongoing projects}

Currently learning about machine learning algorithms, and adapting extreme value statistics to regression problems.

\subsection*{Ph.D. Thesis}

Here you can find the \href{/files/Oral_slides-10.pdf}{\emph{slides}} and the final \href{/files/these_archivage_3701601.pdf}{\emph{manuscript}} of my Ph.D. thesis entitled "Assessing the time dependence of multivariate extremes for heavy rainfall modeling”.

\end{document}
